Simple Test coexistence

### 2018-06-04 first_simultations.Rmd
Compute CWM

```{r}
devtools::load_all()
#### Keep stable for all
patches  <- 25   # Number of patches
species  <- 25   # Number of species
time     <- 150	 # Length of model run (generations)
initpop  <- 150   # initial population size
n_traits <- 1    # number of traits
k        <- 1.05 # Niche height
c        <- 0.25 # Niche breadth

# Competition + Dispersion coefficients
A =  0.0005	# Alpha scalar 
d = 0.01 # Dispersal percentage

@@

plot_patches = plot_grid(p5_grow, p5_comp, p5_both, p15_grow, p15_comp,
                         p15_both, ncol = 3, nrow = 2)
```

>>>>

```{r}
devtools::load_all()
#### Keep stable for all
patches  <- 25   # Number of patches
species  <- 25   # Number of species
time     <- 150	 # Length of model run (generations)
initpop  <- 150   # initial population size
n_traits <- 1    # number of traits
k        <- 1.45 # Niche height
c        <- 10 # Niche breadth

# Competition + Dispersion coefficients
A =  0.0005	# Alpha scalar 
d = 0.5 # Dispersal percentage

@@

plot_patches = plot_grid(p5_grow, p5_comp, p5_both, p15_grow, p15_comp,
                         p15_both, ncol = 3, nrow = 2)
plot_patches
```

## Compute CWM & CWV

```{r}
compute_cwm = function(simulation_routine, trait_df = traits) {
    cwm_df = (simulation_routine$compo[,,150] / rowSums(simulation_routine$compo[,,150])) %*% trait_df

    cwm_df = as.data.frame(cwm_df)
    cwm_df = tibble::rownames_to_column(cwm_df, "patch")
    cwm_df$env      = seq(patches)

    return(cwm_df)
}

both_cwm = compute_cwm(single_trait_both, traits)
colnames(both_cwm)[2] = c("both_cwm")
growth_cwm = compute_cwm(single_trait_growth, traits)
colnames(growth_cwm)[2] = c("growth_cwm")
compet_cwm = compute_cwm(single_trait_compet, traits)
colnames(compet_cwm)[2] = c("compet_cwm")

all_cwm = merge(both_cwm, growth_cwm, c("patch", "env"))
all_cwm = merge(all_cwm, compet_cwm, c("patch", "env"))
all_cwm = tidyr::gather(all_cwm, "cwm_type", "cwm_value", dplyr::contains("cwm"))

plot_cwm = ggplot(all_cwm, aes(env, cwm_value, color = cwm_type)) +
    geom_abline(slope = 1, intercept = 0) +
    geom_point() +
    labs(x = "Environmental Value",
         y = "Community Weighted Mean",
         subtitle = "Timestep: 150, Trait Both") +
    scale_color_discrete(labels = c(pred_cwm = "Optimal\nTrait",
                                    trait1   = "Obs. CWM")) +
    theme_bw()
plot_cwm
```
